\subsection{How to design programs}

This is the first text I'll recommend. The reasons are 2. First, they get the
epistemological approach, as shown by statements as

\begin{quotation}
    Learning to design programs is like learning to play soccer. A player must learn
    to trap a ball, to dribble with a ball, to pass, and to shoot a ball. Once the
    player knows those basic skills, the next goals are to learn to play a position,
    to play certain strategies, to choose among feasible strategies, and, on
    occasion, to create variations of a strategy because none of the existing
    strategies fits.

    A programmer is also very much like an architect, a composer, or a writer. They
    are creative people who start with ideas in their heads and blank pieces of
    paper. They conceive of an idea, form a mental outline, and refine it on paper
    until their writings reflect their mental image as much as possible. As they
    bring their ideas to paper, they employ basic drawing, writing, and instrumental
    skills to express certain style elements of a building, to describe a person's
    character, or to formulate portions of a melody. They can practice their trade
    because they have honed their basic skills for a long time and can use them on
    an instinctive level.
    \cite{education:felleisen__htdp}
\end{quotation}

But the main reason is that they place an emphasis on a design recipe. 

\begin{quotation}
Design recipes are the equivalent of soccer ball handling techniques, writing
techniques, techniques of arrangements, and drawing skills. A single design
recipe represents a point of the program design space. We have studied this
space and have identified many important categories. This book selects the most
fundamental and the most practical recipes and presents them in increasing order
of difficulty.
\cite{education:felleisen__htdp}
\end{quotation}

Not only the book provides all that, they also couple it with its program
environment and editor, a tool know as DrScheme. It is a professional as well as
an educational leverage, and its use along with the text is imperative for
getting the full experience.\cite{programming:falleisen__drscheme}

